---
title: "Livestock assessment"
author: "Jacob Malcom, DOW"
date: "12/17/2016"
output: 
  html_document:
    theme: yeti
    css: styles.css
runtime: shiny
---

```{r setup, include=FALSE}
library(dplyr)
library(DT)
library(shiny)
knitr::opts_chunk$set(echo = TRUE)
load("live_graze.rda")
load("missing_spp.rda")
```

## Summary

The following table is a summary of full-text searches of >3,500 
_Federal Register_ documents for the terms:

- 'livestock';
- 'sheep';
- 'cattle';
- 'trampl* (to match 'trample,' 'trampling,' and other related words);
- 'graz*' (e.g., grazing and graze);
- 'sediment' (e.g., sedimentation); or
- 'water quality'.

After searching all documents, the document set was first filtered to exlude 
those with 'propos*' (e.g., proposed or proposal) or 'Notice of Review' in the 
title. The next filter included  those docs with 'endangered,' 'threatened,' 
'end,' or 'thr.' in the title.  Unfortunately, you'll see that
some number of docs are for critical habitat designation (final rules). Because
a significant number of CH designations were done concurrent with listing, 
filtering out docs whose title includes 'critical habitat' increases the false
negative rate. (A more complex set of searches might have a very high return,
but I can't get to it at the moment.) In other words, the results are not perfect,
but are a good start.

## Coverage

This document set covers 1,598 domestic listed species...or at least the documents
are linked on 1,598 species' pages on [ECOS](http://ecos.fws.gov). There are 
currently 1,611 listed species, so at least 13 species may lack final listing 
rules in this document set. Those species are listed at the bottom of the page, 
below the main table, to help you track down missing documents. Could the 
number be more or less than this? It probably it, but I hope this is a decent
starting point.

## Usage

The following are my thoughts on how to work through this information, but 
definitely feel free to adjust as you see fit! I would start by sorting the
table by `n_hit`, from high to low, to get the docs that discuss cattle-
related terms most first. (That is, I'm assuming that more hits of the terms
means that the threat is more extensively discussed.)

Next, I would work down the table and look at the first column, `Title` to see 
if the title suggests it really is a final listing rule. Some are not (see above)!
To evaluate the documents individually, you can click the link in either the 
second column (`Link`) _or_ go to the original FWS version of the document using
the link in the far-right column. (Note that the FWS-provided version may not
have embedded text in the PDF, and may therefore not be searchable.) 
After the first few documents - when it's pretty clear that livestock / cattle /
and other effects are being discussed, comparing the number of hits to each search
pattern will probably provide some helpful hints.

_Note_: Every column can be sorted (arrows) or searched (boxes). 

```{r echo = FALSE}
live_graze$Link <- paste0("<a href='", 
                          live_graze$Link, 
                          "' target='_blank'>Link</a>")
live_graze$Orig_URL <- paste0("<a href='", 
                              live_graze$Orig_URL, 
                              "' target='_blank'>FWS Link</a>")
live_graze$Date <- as.Date(live_graze$Date)
DT::renderDataTable(
  live_graze,
  filter = "top",
  extensions = "Buttons",
  options = list(searching = "true",
                 dom = "Bfrtip",
                 pageLength = 25,
                 buttons = c('copy', 'csv', 'excel'),
                 autoWidth = FALSE), 
  escape = FALSE
)
```

## Missing species

These species are not associated with any of the documents in the table above:

```{r echo = FALSE}
DT::renderDataTable(
  missing_spp,
  options = list(searching = "true",
                 dom = "Bfrtip",
                 pageLength = 50,
                 buttons = c('copy', 'csv', 'excel'),
                 autoWidth = FALSE), 
  escape = FALSE
)
```

```{r echo = FALSE}
# tmp <- unlist(lapply(live_graze$Species, paste, collapse = "; "))
# live_graze$Species <- tmp
# readr::write_tsv(live_graze, path = "livestock_queries.tsv")
```

<br>
<hr>
<br>
